First steps towards a formalization of Forcing

### 2018-07-13 LSFA/first_steps_into_forcing.tex
typo

  Given a transitive set $M$, we define its generic extension $M[G]$,
  the canonical names for elements of $M$, and finally show that if $M$
  satisfy the axiom of pairing, then $M[G]$ also does.
\end{abstract}
\begin{keyword}
Isabelle/ZF, forcing, preorder, Rasiowa-Sikorski lemma, names, generic extension.
\end{keyword}
\end{frontmatter}

>>>>

  Given a transitive set $M$, we define its generic extension $M[G]$,
  the canonical names for elements of $M$, and finally show that if $M$
  satisfies the axiom of pairing, then $M[G]$ also does.
\end{abstract}
\begin{keyword}
Isabelle/ZF, forcing, preorder, Rasiowa-Sikorski lemma, names, generic extension.
\end{keyword}
\end{frontmatter}
